The K2 Bright Star Survey

### 2019-05-16 paper/ms.tex
new updates

\begin{figure*}
\plotone{rho_leo_pub.pdf}
\label{fig:rholeo}
\caption{Summary plots for \textsc{k2sc}-corrected final halo light curve for $\rho$~Leonis. The top three panels illustrate \textsc{k2sc} systematics correction: at the top, flux minus the GP time trend (blue dots) with GP $x,y$ trend superimposed (orange line); in the middle, flux minus GP $x,y$ components with GP time trend superimposed, and in green, a fifteenth-order polynomial trend; at the bottom the `whitened' light curve with flux minus both GP components. Middle two panels: log-flux map (left) and halo log-weight map (right). Bottom two panels: periodograms in linear (top) and log (bottom) units of the residuals of the corrected light curve minus the long term polynomial trend. Plots of this form are available in supplementary online material for all long-cadence stars, together with similar plots for all short-cadence stars but without \textsc{k2sc}. The period at maximum power (16\,d) is marked on all plots, though for $\rho$~Leonis all variability is consistent with red noise \citep{bowman19}.}
\end{figure*}

@@

\begin{figure*}
\plotone{planets_halo_pdc.pdf}
\label{fig:planets}
\caption{The eight transiting single-planet systems in \ktwo Campaign~6 in the magnitude range $11.5 < Kp < 12.5$, with PDC light curves (blue) and TV-min light curves (orange) overlaid. These have been identically \textsc{k2sc}-corrected, whitened, outlier-clipped, folded and binned as described in Section~\ref{sec:benchmarking}. The depths and shapes of the transits agree closely except for EPIC~212460519, for which the TV-min transit is slightly shallower, and EPIC~212555594, for which TV-min is significantly shallower.}
\end{figure*}

@@

\begin{figure}
\plotone{halo_pdc_comparison.png}
\label{fig:halovspdc}
\caption{Correlation diagram of the \texttt{lightkurve}-computed 6.5\,hr CDPP for \ktwo Campaign~6 stars in the magnitude range $11.5 < Kp < 12.5$, as processed with the PDC pipeline ($x$-axis) and TV-min pipeline ($y$-axis), both after correction and whitening with \textsc{k2sc}. The severe outliers where halo significantly outperforms PDC are shown by individual inspection to consist of stars for which there is contamination, or for which the SAP aperture assigned by the \kepler pipeline is significantly smaller than the PSF.}
\end{figure}

\begin{figure}
\plotone{halo_pdc_histograms.pdf}
\label{fig:cdpphists}
\caption{}
\end{figure}

@@

\subsection{Oscillating Red Giants}
\label{sec:rgs}
31 of the evolved stars in our sample have detectable stochastically-excited solar-like acoustic oscillations. In the asymptotic limit, these consist of a comb of modes separated by the large frequency separation \Dnu, approximately the sound-crossing-time of the star, with a Gaussian envelope centred on the frequency of maximum power \numax, which scales with the acoustic cutoff frequency at the star's surface. These can be used to constrain stellar fundamental parameters, and detailed studies of the deviations from this asymptotic limit for acoustic $p$-modes, for example due to their interaction with gravity-wave $g$-modes, can be used to accurately determine the stellar evolutionary state, for example to distinguish hydrogen shell burning red giant branch from helium core burning red clump stars.

@@

>>>>

\begin{figure*}
\plotone{rho_leo_pub.pdf}
\caption{Summary plots for \textsc{k2sc}-corrected final halo light curve for $\rho$~Leonis. The top three panels illustrate \textsc{k2sc} systematics correction: at the top, flux minus the GP time trend (blue dots) with GP $x,y$ trend superimposed (orange line); in the middle, flux minus GP $x,y$ components with GP time trend superimposed, and in green, a fifteenth-order polynomial trend; at the bottom the `whitened' light curve with flux minus both GP components. Middle two panels: log-flux map (left) and halo log-weight map (right). Bottom two panels: periodograms in linear (top) and log (bottom) units of the residuals of the corrected light curve minus the long term polynomial trend. Plots of this form are available in supplementary online material for all long-cadence stars, together with similar plots for all short-cadence stars but without \textsc{k2sc}. The period at maximum power (16\,d) is marked on all plots, though for $\rho$~Leonis all variability is consistent with red noise \citep{bowman19}.}
\label{fig:rholeo}
\end{figure*}

@@

\begin{figure*}
\plotone{planets_halo_pdc.pdf}
\caption{The eight transiting single-planet systems in \ktwo Campaign~6 in the magnitude range $11.5 < Kp < 12.5$, with PDC light curves (blue) and TV-min light curves (orange) overlaid. These have been identically \textsc{k2sc}-corrected, whitened, outlier-clipped, folded and binned as described in Section~\ref{sec:benchmarking}. The depths and shapes of the transits agree closely except for EPIC~212460519, for which the TV-min transit is slightly shallower, and EPIC~212555594, for which TV-min is significantly shallower.}
\label{fig:planets}
\end{figure*}

@@

\begin{figure}
\plotone{halo_pdc_comparison.png}
\caption{Correlation diagram of the \texttt{lightkurve}-computed 6.5\,hr CDPP for \ktwo Campaign~6 stars in the magnitude range $11.5 < Kp < 12.5$, as processed with the PDC pipeline ($x$-axis) and TV-min pipeline ($y$-axis), both after correction and whitening with \textsc{k2sc}. The severe outliers where halo significantly outperforms PDC are shown by individual inspection to consist of stars for which there is contamination, or for which the SAP aperture assigned by the \kepler pipeline is significantly smaller than the PSF.}
\label{fig:halovspdc}
\end{figure}

Histograms of the CDPPs of the SAP, PDC and halo light curves with and without \textsc{k2sc} are displayed in Figure~\ref{fig:cdpphists}. We see that both halo and PDC significantly outperform SAP, with halo performing better than PDC with no additional correction. Nevertheless, after \textsc{k2sc}, we find that the best PDC lightcurves have a smaller CDPP than the best similarly pointing-corrected halo. We conjecture that PDC with its improved calibration for common-mode systematics and blended/background light is correcting for effects that halo, as a single-star and instrument-agnostic method, does not.

\begin{figure}
\plotone{halo_pdc_histograms.pdf}
\caption{Histograms of the \texttt{lightkurve}-computed 6.5\,hr CDPP for five different pipelines applied to \ktwo Campaign~6 stars in the magnitude range $11.5 < Kp < 12.5$: SAP (purple dashed), PDC with (blue solid) and without (blue dashed) \textsc{k2sc}, and TV-min with (orange solid) and without (orange dashed) \textsc{k2sc}.}
\label{fig:cdpphists}
\end{figure}

@@

\subsection{Oscillating Red Giants}
\label{sec:rgs}
31 of the evolved stars in our sample have detectable stochastically-excited solar-like acoustic oscillations. In the asymptotic limit, these consist of a comb of modes separated by the large frequency separation \Dnu, approximately the sound-crossing-time of the star, with a Gaussian envelope centred on the frequency of maximum power \numax, which scales with the acoustic cutoff frequency at the star's surface. These can be used to constrain stellar fundamental parameters, and detailed studies of the deviations from this asymptotic limit for acoustic $p$-modes, for example due to their interaction with gravity-wave $g$-modes, can be used to accurately determine the stellar evolutionary state, for example to distinguish hydrogen shell burning red giant branch from helium core burning red clump stars. Summary plots for a good example of such a star, $\eta$~Cancri, are shown in Figure~\ref{fig:etacnc}.

@@

\begin{figure*}
\plotone{eta_cnc_pub.pdf}
\caption{Summary plots for \textsc{k2sc}-corrected final halo light curve for the red giant $\eta$~Cancri, in the same format as Figure~\ref{fig:rholeo}. Solar like oscillations are clearly detected with $\numax = 22.9 \pm 0.9$ and $\Dnu = 2.7 \pm 0.03$.}
\label{fig:etacnc}
\end{figure*}
